Measurement Bias from Address Aliasing

### 2014-05-26 paper.tex
Update aslr reference

We also have to ensure we are not affected by measurement bias beyond what we are actually trying to observe, and in general follow best practices on gathering data~\cite{Mytkowicz:2009:WrongData}.
Most importantly, this means keeping the memory address space under control.
For security reasons, addresses of stack, heap and dynamic libraries are often randomized at load time, a technique known as \emph{Address Space Layout Randomization}~\cite{Shackham:2004:ASLR}. % Should maybe have more generic reference
By disabling ASLR, we are able to execute the same program multiple times with identical virtual address spaces.
All experiments are done on a machine under minimal load, and \emph{frequency scaling} is disabled to keep the CPU's clock speed fixed.
Finally, we disable \emph{Hyper-threading}, which reduces the possibility for resource contention between threads.

>>>>

We also have to ensure we are not affected by measurement bias beyond what we are actually trying to observe, and in general follow best practices on gathering data~\cite{Mytkowicz:2009:WrongData}.
Most importantly, this means keeping the memory address space under control.
For security reasons, addresses of stack, heap and dynamic libraries are often randomized at load time, a technique known as \emph{Address Space Layout Randomization}~\cite{Pax:ASLR,Bhatkar:AddressObfuscation}. 
By disabling ASLR, we are able to execute the same program multiple times with identical virtual address spaces.
All experiments are done on a machine under minimal load, and \emph{frequency scaling} is disabled to keep the CPU's clock speed fixed.
Finally, we disable \emph{Hyper-threading}, which reduces the possibility for resource contention between threads.
